BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-03 tex/3-algorithms.tex
3.5 close to done.

% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

\TODO{Assumption is not a good word, we are based on facts from previous work.}

@@

% Embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. Therefore algorithm \ref{extractionAlgo} \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\subsection{Extraction rules and string similarity}
\label{extractionrulesandstringsimilarity}

@@

% algo 1 is quadratic
With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time. First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.

@@

% End of proof
To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all its inner loop computations other than bigrams of \emph{node.text} can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration is one. Each \emph{quotient of similarity} computation requires one bigram intersection and three bigram length computations. Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations can be done in constant time.

@@

% Intro
In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction. This subsection presents variations on the general extraction
\label{presentsvariationsonthegeneralextraction}techniques presented before. \TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

% Authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists of adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

% Dates, authors
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution is to use multiple \emph{target} strings, while extending the rule that we previously described for author extraction. For instance, if the feed indicates that a post was published on
\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a total of 8 target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would certainly by a possible extension of our date extraction algorithm.

% Comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page. To do so we use algorithm \ref{extractionAlgo} with the following modifications:
\begin{enumerate}
  \item Rules that return less HTML nodes than the number of comments on the feed are filtered out.
  \item The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{enumerate}
Our crawler executes this algorithm on each post that present a comment feed overflow, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the first modification by fixing a target number of comments.

>>>>

% html extraction is not trival
extracting metadata and content from html documents is a challenging task. standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}. for instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. in fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}. under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. Therefore algorithm \ref{extractionAlgo} \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
\label{extractionrulesandstringsimilarity}

@@

% into: algo 1 defined
With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.

% algo 1 is quadratic
First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

% linear reformulation
We now present Algorithm \ref{linearAlgo}, linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

% proof
With bigrams computed in a dynamic programming manner, the cumulated time needed to compute \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigram unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigram intersection and three bigram length computations. Over a finite alphabet (we used printable ASCII), bigram sizes have bounded size and each of these operations takes constant time.

@@

% intro
In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction. This subsection presents variations on the general extraction
\label{presentsvariationsonthegeneralextraction}techniques presented before. \TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

% authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

% dates
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution for dates extraction extends authors \code{ScoreFunction} by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original \emph{target} date obtained from the web feed. For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a total of 8 target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score.
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.

\TODO{rush some time complexity analysis and conclude that we can do optimization analogs to algo 2 to obtain linear time on each extraction algo. }
